ps4_models

### 2020-10-29 bi-model.Rmd
modelling

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)
library(brms)
```
```{r}
# remove.packages("rstan")

@@

```{r}
# install.packages("rstan", repos = "https://cloud.r-project.org/", dependencies = TRUE)

```{r}
raw_data <- read_dta("inputs/data/ns20200625/ns20200625.dta")
# Add the labels
raw_data <- labelled::to_factor(raw_data)
```
```{r}
colnames(raw_data)
```

```{r}
reduced_data <- 
  raw_data %>% 
  select(vote_intention,
         vote_2020,
         state,
         race_ethnicity,
         age,
         gender,
         household_income,
         education
  )

reduced_data <- reduced_data[complete.cases(reduced_data), ]

@@

@@

total_rows <- nrow(reduced_data)
table(reduced_data$vote_2020)

reduced_data
```
```{r}
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.9)

training <- data[0:boundary,]
model <- brm(formula = vote_2020 ~ (1|state) + (1|race_ethnicity) + (1|gender) + 
                          (1|household_income) + (1|education), 
             data = training,
             family = bernoulli(),

                   )
```

```{r}
testing <- data[boundary:total_rows,]

probability <- predict(model, newdata = training, "probs")
column_index <- max.col(probability, tie="random")

testing_predictions <- colnames(probability)[column_index]
testing_ground_truth <- training %>% pull(vote_2020)
accuracy(testing_ground_truth, testing_predictions)

>>>>

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)
library(brms)
library(tidybayes)
library(statebins)
```
```{r}
post_strat <- read_dta("inputs/data/usa_00001.dta")
# Add the labels
post_strat <- labelled::to_factor(post_strat)
```

```{r}
factor(post_strat$age)

@@

```{r}
raw_data <- read_dta("inputs/data/ns20200625/ns20200625.dta")
# Add the labels
raw_data <- labelled::to_factor(raw_data)
```
```{r}
raw_data$education
```

```{r}
reduced_data <- 
  raw_data %>% 
  select(vote_2020,
         state,
         race_ethnicity,
         age,
         gender,
         education
  )

# reduced_data <- reduced_data[complete.cases(reduced_data$vote_2020), ]

@@

# reduced_data$age <- reduced_data[reduced_data$age <= 29,] <- "18-29"
# reduced_data$age <- reduced_data[reduced_data$age > 29 &
#                                          reduced_data$age <= 44,] <- "30-44"
# reduced_data$age <- reduced_data[reduced_data$age > 44 &
#                                          reduced_data$age <= 60, ] <- "45-60"
# reduced_data$age <- reduced_data[reduced_data$age > 60,] <- "60+"

reduced_data$age_group <- cut(reduced_data$age, breaks = c(18, 29, 44, 60, 200),
                              labels = c("18-29","30-44","45-60","60+" ), 
                              right=FALSE)

@@

total_rows <- nrow(reduced_data)
table(reduced_data$vote_2020)
table(reduced_data$age_group)
reduced_data
```
```{r}
set.seed(50)
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.95)

training <- data[0:boundary,]
```

```{r}

model <- brm(formula = vote_2020 ~ state + race_ethnicity + gender + education +
               age_group, 
             data = training,
             family = bernoulli(),
             control = list(adapt_delta = .99, 
                            max_treedepth = 15),
             chains = 3,
             iter = 2000,
             cores = 2
)
```

```{r}
saveRDS(model, file = "model/3chain2kiter.rds")

# readRDS("model/3chain2kiter.rds)
```

```{r}
summary(model)
```

```{r}
testing <- data[boundary:total_rows,]
testing$vote_num <- if_else(testing$vote_2020 == "Donald Trump", 0, 1 )
# probability <- model %>% add_predicted_draws(newdata = testing)

# training <- data[0:boundary,]
# training$vote_num <- if_else(training$vote_2020 == "Donald Trump", 0, 1 )

probability <- predict(model, type = "response", newdata = testing)
probability <- if_else(probability[,1] >0.5,1,0)

testing$probs <- probability

testing <- testing %>% mutate(acc = probs==vote_num)

table(testing$acc)

# nrow(testing)
# 
# nrow(probability)
# summary(model)
```
